Checkpoint 4

### 2020-04-28 Checkpoint 4.Rmd
graphs

# Quinn plots stuff
```{r}
a<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")

>>>>

# Quinn plots stuff

```{r}
Finaldata<-read.csv("time_series_final_Data.csv")

```
```{r} 
Finaldata <- Finaldata %>% select(-c(X)) 
Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
```

```{r}
Finaldata%>%
  mutate(perc_population_positive = positive/total_population)%>%
  group_by(State)%>%
  mutate(mean_corona_interest = mean(ChinaVirusInterest),
         max = max(ChinaVirusInterest),
         median = median(ChinaVirusInterest))%>%
  ggplot(aes(x = mean_corona_interest, y = perc_population_positive, color = percent_asian))+
  geom_point()+
  scale_colour_gradient2(low = "blue", mid = "lightblue", high = "red")
```

```{r}
a<- ggplot(Finaldata, aes(x = ChinaVirusInterest, fill = as.factor(State))) + 
  geom_density(alpha = 0.5)+ ggtitle("China Virus Density by State")
